1-methods-toys

### 2017-09-07 analysis_output/1-methods-toys.Rmd
fixed...... a lot......

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_descriptions <- list(
  waterfall=list(),
  scorpius=list(),
  slingshot=list(),
  gpfates=list(nfates=1),
  stemid=list(clustnr=10, bootnr=10, pdishuf=10),
  tscan=list(),
  embeddr=list(nn_pct = 2),
  celltree_gibbs=list(sd_filter = 0),
  celltree_maptpx=list(sd_filter = 0),
  celltree_vem=list(sd_filter = 0),
  scuba=list(),
  slicer = list(min_branch_len=50),
  monocle_ddrtree=list(),
  wishbone = list(branch=F),
  pseudogp = list(iter=100, initialise_from="principal_curve"),
  mpath = list(numcluster=6),
  random_linear=list()
)

@@

```{r}
results <- purrr::map(names(method_descriptions), function(method_name) {
  library(dyneval)

  cat("Processing ", method_name, "\n", sep="")
  method <- get(paste0("description_", method_name))()
  method_params <- method_descriptions[[method_name]]

@@

  factory(function() {
    dyneval:::execute_evaluation(tasks, method, method_params, metrics = metric_names, suppress_output = F)
  }
  )()
})
```

@@

```{r}
scores %>% filter(errored)
```

>>>>

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_params <- list(
  waterfall=list(),
  scorpius=list(),
  slingshot=list(),
  gpfates=list(nfates=1),
  stemid=list(clustnr=10, bootnr=10, pdishuf=10),
  tscan=list(),
  embeddr=list(nn_pct = 2),
  celltree_gibbs=list(sd_filter = 0),
  celltree_maptpx=list(sd_filter = 0),
  celltree_vem=list(sd_filter = 0),
  scuba=list(),
  slicer = list(min_branch_len=50),
  monocle_ddrtree=list(),
  wishbone = list(branch=F),
  pseudogp = list(iter=100, initialise_from="principal_curve"),
  mpath = list(numcluster=6),
  random_linear=list()
)
method_names <- names(method_params)

method_descriptions <- map(method_names, ~get(paste0("description_", .))()) %>% set_names(method_names)

@@

```{r}
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

  cat("Processing ", method_name, "\n", sep="")
  method <- method_descriptions[[method_name]]
  params <- method_params[[method_name]]

@@

  factory(function() {
    dyneval:::execute_evaluation(tasks, method, params, metrics = metric_names, suppress_output = F)
  }
  )()
})
```

@@

```{r}
scores %>% filter(errored)

print(scores$error)
```
